### 2025-02-20 paper/sections/other/constraints.qmd
solid observations and progress today

    # Data:
    data = LinearlySeparable(
        n_train=5000,
        batchsize=50,
        mutability=constraint
    )
    global ce_data = get_ce_data(data)
    val_size = data.n_validation / (data.n_validation + data.n_train)
    train_set, val_set, _ = train_val_split(data, ce_data, val_size)

@@

    # Objective:
    generator = ECCoGenerator()
    opt_state = Flux.setup(Descent(), model)
    conv = DecisionThresholdConvergence(decision_threshold=0.95, max_iter=25)

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 50,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=1000,
        convergence=conv, 
        verbose=3
    )

>>>>

    # Data:
    data = LinearlySeparable(
        n_train=3000,
        batchsize=50,
        mutability=constraint
    )
    global ce_data = get_ce_data(data)
    val_size = data.n_validation / (data.n_validation + data.n_train)
    train_set, val_set, _ = train_val_split(data, ce_data, val_size)

@@

    # Objective:
    generator = ECCoGenerator()
    opt_state = Flux.setup(Descent(), model)
    conv = DecisionThresholdConvergence(decision_threshold=0.95, max_iter=30)

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 100,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=1000,
        convergence=conv, 
        verbose=3
    )
